Regional and Urban Economics

### 2023-02-18 Retail Agglomerationextra.qmd
..

For example faster transportation can increase convenience of commuting, increasing rent commuters from the city centre are willing to pay, and therefore increasing the area of developed land without this being necessary corresponding to an increase in population.
As distance increases, communication networks become important allowing the growth of sub centres to functions as self organising systems.

@@

Subsequently, when using the dentist income (y) and comparing the distance from the mall (x), signs of patterns emerge showing that income is greater when the dentist is placed closer to the shopping mall.
Furthermore, decreasing as the distance gets bigger.

However, when the distance reach around 10km from the mall the income starts to increase before it then starts to decrease again around 20km.
The Keynesian theory suggest that this pattern might take place as the transportation cost for individuals further away from the Shopping mall does not increase to much by travelling the extra distance.
Hotelling also describes this case where the consumer are willing to travel further to reach a certain central place.

>>>>

@@

Furthermore, when using the dentist income (y) and comparing the distance from the mall (x), signs of patterns emerge showing that income is greater when the dentist is placed closer to the shopping mall.
Furthermore, decreasing as the distance gets bigger.

Faster transportation can increase convenience of commuting, increasing rent commuters from the city centre are willing to pay, and therefore increasing the area of developed land without this being necessary corresponding to an increase in population.
As distance increases, communication networks become important allowing the growth of sub centres to functions as self organising systems.

Subsequently, when the distance reach around 10km from the mall the income starts to increase before it then starts to decrease again around 20km.
The Keynesian theory suggest that this pattern might take place as the transportation cost for individuals further away from the Shopping mall does not increase to much by travelling the extra distance.
Hotelling also describes this case where the consumer are willing to travel further to reach a certain central place.
